---
title: "Comparison of MFD metadata releases"
author: "F. Delogu"
date: "as.Date(now())"
output:
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
    toc_collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
params:
  debug: no
---

<style type="text/css">
body, td {
   font-size: 10pt;
   text-align: justify
}
code.r{
  font-size: 8pt;
}
pre {
  font-size: 8pt
}
</style>

# Setup

## Load libraries
```{r load libraries, message=F, warning=F, echo=params$debug}
library(tidyverse)
library(openxlsx)
library(knitr)

options(width = 500)
```

## Set the environment
```{r setup, echo=params$debug}
options(stringsAsFactors = F, gsubfn.engine = "R")

Sys.setenv("LANGUAGE"="En")

wd <- getwd()

releases.path <- paste0(wd, '/../../analysis/releases')
downloads.path <- paste0(wd, '/../../data/downloads')

eval_debug <- params$debug
```

This section is meant for internal use and debugging, if you are interest in seeing the code please knit again the document setting the "debug" flag to "true". 

For the generation of this document the parameters were set as:
```{r print params, echo=eval_debug}
data.frame(param=c("debug"), value=c(eval_debug)) %>%
  kable()
```

## Custom functions

### Load functions
```{r load custom functions, message=F, warning=F, echo=eval_debug}
source(paste0(wd, "/mfd_report_test_routine.R"))
```

## Load data

### Read data table
Read al the time-stamped MfD metadata releases
```{r, echo=eval_debug}
file.paths <- list.files(releases.path, pattern="*.xlsx", full.names=TRUE)
tables <- lapply(file.paths, read.xlsx)
fnames <- basename(file.paths)
```

### Split and retrieve time stamps
```{r, echo=eval_debug}
dates.db <- str_remove(fnames[grep("mfd_db", fnames)], "_mfd_db.xlsx")
tables.db <- tables[grep("mfd_db", fnames)]
```

# Analysis

## Summary of releases
```{r, echo=eval_debug, warning=F, message=F}
union.names <- reduce(lapply(tables.db, names), union)
names.order <- c("fieldsample_barcode", "sample_type", "received", "sampling_date", "latitude", "longitude", "habitat_type", "habitat_typenumber", "sitename", "mfd_sampletype", "mfd_areatype", "mfd_hab1", "mfd_hab2", "mfd_hab3", "sampling_comment", "project_id")

tables.summ <- list()

summ.indices <- function(data_table, date_release, indices=NA){
  tmp <- names(data_table)
  tmp <- indices[indices%in%tmp]
  tmp <- summarise_metadata(data_table, indices=tmp) %>% select(field, present, `present [%]`) %>% `colnames<-`(c("field", paste0(date_release, " [N]"), paste0(date_release, " [%]")))
  return(tmp)
}

tables.summ <- reduce(mapply(summ.indices, tables.db, dates.db, MoreArgs=list(indices=names.order), SIMPLIFY = F), full_join) %>%
  arrange(factor(field, levels=names.order))

tables.summ %>% kable(digits = 1)
```

## Differences of releases
```{r, echo=eval_debug, warning=F, message=F}
names.summ <- names(tables.summ)

diff.names <- c()
diff.cols <- c()
for(i in 4:length(tables.summ)){

    split.name <- unlist(str_split(names.summ[i] , " "))
  new.name <- paste0(split.name[1], " Δ ", split.name[2])
  diff.names <- c(diff.names, new.name)

  j <- i - 2
  diff.cols <- c(diff.cols, tables.summ[,i] - tables.summ[,j])
}

diff.cols <- as.data.frame(diff.cols)
colnames(diff.cols) <- diff.names

new.names <- c()
new.names <- c(new.names, names.summ[1:3])
for(i in 4:length(tables.summ)){
  new.names <- c(new.names, names.summ[i])
  new.names <- c(new.names, diff.names[i-3])
}

tables.summ <- cbind(tables.summ, diff.cols)[,new.names]

tables.summ %>% kable(digits = 1)
```

# Output

## Print difference tables
```{r, echo=eval_debug, warning=F, message=F}

if(file.exists(paste0(releases.path, "/", unlist(str_split(names.summ[length(names.summ)], " "))[1], "_diff.xlsx"))){
    file.remove(paste0(releases.path, "/", unlist(str_split(names.summ[length(names.summ)], " "))[1], "_diff.xlsx"))
}

wb <- openxlsx::createWorkbook()
    
openxlsx::addWorksheet(wb, "variables")
header_style <- openxlsx::createStyle(textDecoration = "Bold")
openxlsx::writeData(wb, "variables", tables.summ, headerStyle = header_style)

openxlsx::saveWorkbook(wb, paste0(releases.path, "/", unlist(str_split(names.summ[length(names.summ)], " "))[1], "_diff.xlsx"))
```

## Plot time-courses
```{r, echo=eval_debug, warning=F, message=F}
entires.time <- tables.summ %>%
  column_to_rownames(var="field") %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column(var="relsease") %>%
  rowwise() %>%
  mutate(coords=min(latitude, longitude)) %>%
  t() %>%
  as.data.frame() %>%
  `colnames<-`(unlist(.[1,])) %>%
  rownames_to_column(var="field") %>%
  filter(field%in%c("sampling_date", "coords", "sitename", "mfd_sampletype", "mfd_areatype", "mfd_hab1", "mfd_hab2", "mfd_hab3")) %>%
  mutate(field = factor(field, levels=c("sampling_date", "coords", "sitename", "mfd_sampletype", "mfd_areatype", "mfd_hab1", "mfd_hab2", "mfd_hab3"))) %>%
  pivot_longer(-field) %>%
  mutate(value=as.numeric(value)) %>%
  filter(!str_detect(name, "Δ")) %>%
  separate(name, into = c("name", "unit"), sep = " ") %>%
  filter(unit=="[N]") %>%
  ggplot(aes(x=name, y=value, group=field, color=field)) +
  geom_line() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(x="Release date", y="Filled entries")

entires.time
ggsave(paste0(releases.path, "/entires_time.png"), entires.time, width=5, height=3.75)
```
