---
title: "MFD update metadata for revision"
author: "F. Delogu"
date: "as.Date(now())"
output:
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
    toc_collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
params:
  debug: no
  debug2: no
  internal: yes
  release: yes
---

<style type="text/css">
body, td {
   font-size: 10pt;
   text-align: justify
}
code.r{
  font-size: 8pt;
}
pre {
  font-size: 8pt
}
</style>

# Setup

## Install libraries

Installing libraries not included in the mamba environment.
```{r install libraries, message=F, warning=F, echo=params$debug}
if(!require("devtools")) install.packages("devtools")
```

## Load libraries
```{r load libraries, message=F, warning=F, echo=params$debug}
library(tidyverse)
library(lubridate)
library(openxlsx)
library(knitr)

options(stringsAsFactors = F,
        width = 500,
        gsubfn.engine = "R",
        timeout = max(1000, getOption("timeout")))
```

## Set the environment
```{r setup, echo=params$debug}
options(stringsAsFactors = F, gsubfn.engine = "R")

Sys.setenv("LANGUAGE"="En")

wd <- getwd()

ontology.path <- paste0(wd, '/../../data/ontology/2025-02-11_mfd-habitat-ontology.xlsx')
downloads.path <- paste0(wd, '/../../data/downloads')
metadata.path <- paste0(wd, '/../../data/metadata')

mfd_projects.path <- paste0(wd, '/../../data/results/mfd_projects.xlsx')
minimal_indices_explanation <- paste0(metadata.path, '/general/minimal_metadata_descriptors.xlsx')
reformat.metadata.path <- paste0(wd, '/../../analysis/metadata')

releases.path <- paste0(wd, '/../../analysis/releases')

release_indices <-c(
    "fieldsample_barcode",
    "project_id",
    "sampling_method",
    "sampling_date",
    "latitude",
    "longitude",
    "habitat_typenumber",
    "sitename",
    "mfd_sampletype",
    "mfd_areatype",
    "mfd_hab1",
    "mfd_hab2",
    "mfd_hab3",
    "coords_reliable",
    "cell.10km_representative",
    "cell.10km",
    "cell.1km",
    "BioProject",
    "BioSample",
    "Metagenome",
    "Metagenome_assembly",
    "EUK_operon",
    "BAC_operon",
    "UMI_16SrRNA",
    "sampling_comment",
    "extraction_method",
    "extraction_id1",
    "extraction_id2",
    "extractionplate_id1",
    "extractionplate_id2",
    "extraction_row1",
    "extraction_row2",
    "extraction_col1",
    "extraction_col2",
    "extraction_conc1",
    "extraction_conc2",
    "library_method",
    "library_id1",
    "library_id2",
    "libraryplate_id1",
    "libraryplate_id2",
    "library_row1",
    "library_row2",
    "library_col1",
    "library_col2",
    "library_conc1",
    "library_conc2",
    "sequencing_method",
    "sequencing_id1",
    "sequencing_id2",
    "internal_name",
    "before_total_reads",
    "after_total_reads",
    "passed_filter_reads",
    "corrected_reads",
    "low_quality_reads",
    "too_many_N_reads",
    "too_short_reads",
    "too_long_reads",
    "before_total_bases",
    "before_q20_bases",
    "before_q30_bases",
    "after_total_bases",
    "after_q20_bases",
    "after_q30_bases",
    "corrected_bases",
    "before_read1_mean_length",
    "before_read2_mean_length",
    "after_read1_mean_length",
    "after_read2_mean_length",
    "before_q20_rate",
    "before_q30_rate",
    "after_q20_rate",
    "after_q30_rate",
    "duplication_rate",
    "before_gc_content",
    "after_gc_content",
    "peak_length")


sra_map <- read_tsv(paste0(metadata.path, "/general/2025-04-14_MFD_NCBI_meta 1.tsv"), col_names = T)

lab_cols <- read_tsv(paste0(metadata.path, "/general/2025-05-26_MFD_laboratory_metadata_new_cols_only.tsv"), col_names = T)

eval_debug <- params$debug
eval_debug2 <- params$debug2
eval_internal <- params$internal
eval_release <- params$release
```

This section is meant for internal use and debugging, if you are interest in seeing the code please knit again the document setting the "debug" flag to "true". Optionally, set "debug2" as "true" to see also the code to generate the debug headings and text.

For the generation of this document the parameters were set as:
```{r print params, echo=eval_debug}
data.frame(param=c("debug", "debug2", "internal", "release"), value=c(eval_debug, eval_debug2, eval_internal, eval_release)) %>%
  kable()
```

### Load functions
```{r load custom functions, message=F, warning=F, echo=eval_debug}
source(paste0(wd, "/mfd_report_test_routine.R"))
```

## Load data

### Load the metadata form the first submission
```{r load metadata first submission, message=F, warning=F, error=F, echo=eval_debug}
mfd_db <- read.xlsx(paste0(releases.path, "/2024-02-13_mfd_db.xlsx"))
```

# Subproject curation for second submission

## P18_1
```{r P18_1, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P18_1"

mfd_db <- mfd_db %>%
  mutate(mfd_sampletype      = ifelse(project_id == pid, "Other", mfd_sampletype)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P18_2
```{r P18_2, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P18_2"

mfd_db <- mfd_db %>%
  mutate(mfd_sampletype      = ifelse(project_id == pid, "Other", mfd_sampletype)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P16_2
```{r P16_2, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P16_2"

mfd_db <- mfd_db %>%
  mutate(mfd_sampletype      = ifelse(project_id == pid & mfd_hab3 == "Sandfilter", "Other", mfd_sampletype)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P16_3
```{r P16_3, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P16_3"

mfd_db <- mfd_db %>%
  mutate(mfd_sampletype     = ifelse(project_id == pid &
                                       mfd_hab3 == "Sandfilter" &
                                       !is.na(mfd_hab3),
                                     "Other", mfd_sampletype)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P20_1
```{r P20_1, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P20_1"

mfd_db <- mfd_db %>%
  mutate(mfd_sampletype     = ifelse(project_id == pid &
                                       mfd_sampletype == "Sediment",
                                     "Other", mfd_sampletype),
         mfd_hab2           = ifelse(project_id == pid &
                                       mfd_sampletype == "Water",
                                     "Leachate", mfd_sampletype),
         habitat_typenumber = ifelse(project_id == pid &
                                       mfd_sampletype == "Water",
                                     "6100", habitat_typenumber),
         habitat_typenumber = ifelse(project_id == pid &
                                       mfd_sampletype == "Soil",
                                     "5000", habitat_typenumber)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P25_1
```{r P25_1, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P25_1"

mfd_db <- mfd_db %>%
  mutate(mfd_sampletype     = if_else(project_id == pid &
                                       mfd_sampletype == "Sediment",
                                     "Other", mfd_sampletype),
         habitat_typenumber = if_else(project_id == pid &
                                       mfd_hab2 == "High salinity (saltworks)" &
                                      !is.na(mfd_hab2),
                                     "5200", habitat_typenumber),
         habitat_typenumber = if_else(project_id == pid &
                                       mfd_hab2 == "High chalk concentration (limestone quarry)" &
                                      !is.na(mfd_hab2),
                                     "5300", habitat_typenumber)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P12_1
```{r P12_1, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P12_1"

mfd_db <- mfd_db %>%
  mutate(project_id     = if_else(project_id == pid &
                                       year(sampling_date) == 2014,
                                  "P12_2", project_id)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P04_3
```{r P04_3, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P04_3"

mfd_db <- mfd_db %>%
  mutate(sampling_date     = case_when(project_id == pid & year(sampling_date) == 2020 ~ "2020-02-08",
                                       project_id == pid & year(sampling_date) == 2021 ~ "2021-02-06",
                                       .default = sampling_date)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P04_6
```{r P04_6, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P04_6"

mfd_db <- mfd_db %>%
  mutate(mfd_areatype        = if_else(project_id == pid, "Agriculture (reclaimed lowland)", mfd_areatype)) %>%
  add_ontology(ontology_path = ontology.path)

rm(pid)
```

## P13_3
```{r P13_3, echo=F, message=F, warning=F, error=F, results='asis'}
pid = "P13_3"

mfd_db <- mfd_db %>%
  mutate(mfd_sampletype         = if_else(project_id == pid, "Other", mfd_sampletype),
    habitat_typenumber          = case_when(project_id == pid & habitat_typenumber == "4100" ~ "6100",
                                            project_id == pid & habitat_typenumber == "4200" ~ "6200",
                                            project_id == pid & habitat_typenumber == "4300" ~ "6300",
                                            .default = habitat_typenumber)) %>%
  add_ontology(ontology_path    = ontology.path)

rm(pid)
```

## Extra samples
```{r Extra samples, echo=F, message=F, warning=F, error=F, results='asis'}
mfd_db <- mfd_db %>%
  add_row(project_id = "P11_2", fieldsample_barcode = "MFD10339", habitat_typenumber = "1000", mfd_sampletype = "Sediment", mfd_areatype = "Natural", mfd_hab1 = "Saltwater", coords_reliable = "Yes")
```

## Incorporate comments from invidual tables
```{r Incorporate comments, echo=F, message=F, warning=F, error=F, results='asis'}
project_comments <- c("P10_2", # Stream speed, temperature and some chemicophysical properties (in Danish)
                      "P11_3", # Environmental variables
                      "P06_2", # Depth
                      "P06_1", # Depth, condition (in Danish)
                      "P11_2", # Condition
                      "P12_1", # Depth
                      "P12_2", # Depth
                      "P12_3", # Depth
                      "P13_1", # Capacity
                      "P13_2", # Capacity
                      "P16_2", # Depth
                      "P06_3", # Depth
                      "P09_3", # Depth
                      "P09_4", # Depth
                      "P12_5" # Depth
                      )

get_comments <- function(path_to_comments, pid){
  X <- read.xlsx(paste0(path_to_comments, "/", pid, "/", pid, "_minimal_metadata.xlsx"))
  to_print <- X %>% filter(project_id == pid) %>%
    select(fieldsample_barcode, sampling_comment) %>%
    mutate(sampling_comment = if_else(sampling_comment=="xml:space=\"preserve\"> ", NA, sampling_comment),
           sampling_comment = as.character(sampling_comment)) %>%
    rowwise() %>%
    mutate(sampling_comment = if_else(grepl("xml:space=\"preserve\">", sampling_comment),
                                      gsub("xml:space=\"preserve\">", "", sampling_comment), sampling_comment))
  return(to_print)
}

mfd_comments <- lapply(project_comments,
                       function (x) get_comments(reformat.metadata.path, x)) %>%
  bind_rows()

mfd_db <- mfd_db %>%
  left_join(mfd_comments,
            by = "fieldsample_barcode")
```

## Filter project descriptions only for retained projects
```{r Filter project description, echo=F, message=F, warning=F, error=F, results='asis'}
mfd_projects <- read.xlsx(paste0(releases.path, "/2024-02-13_mfd_projects.xlsx"))

mfd_projects <- mfd_projects %>%
  filter(project_id %in% unique((mfd_db %>% pull(project_id)))) %>%
  select(-metadata_map)
```

## Add SRA accession identifiers
```{r Add SRA id, echo=F, message=F, warning=F, error=F, results='asis'}
mfd_db <- mfd_db %>%
  left_join(sra_map,
            by = "fieldsample_barcode")
```

### Add extra technical columns

```{r, warning=T, echo=eval_debug, eval=T}
mfd_db <- mfd_db %>% 
  full_join(lab_cols,
            by = "fieldsample_barcode")
```

# General outputs

## Output checks

This is the distribution of sample names in the curated metadata:

### Sample duplication check
```{r, warning=T, echo=eval_debug, eval=T}
table(table(mfd_db$fieldsample_barcode))
```

### Retain samples with project numbers
```{r, warning=T, echo=eval_debug, eval=T}
mfd_db <- mfd_db %>%
  filter(!is.na(project_id))
```

## Write output

### Rearange mfd_db columns

```{r, warning=T, echo=eval_debug, eval=T}
mfd_db <- mfd_db[,release_indices]
```

### Formatting and printing function

```{r, warning=T, echo=eval_debug, eval=T}
print_meta <- function(data_table = NA, fname = NA, second_page = NA){
  
  if(file.exists(fname)){
    file.remove(fname)
  }
  
  data_table <- data_table %>%
    mutate(across(everything(), ~if_else(.x=="", NA, .x)))
  
  wb <- openxlsx::createWorkbook()
  
  openxlsx::addWorksheet(wb, "variables")
  header_style <- openxlsx::createStyle(textDecoration = "Bold")
  openxlsx::writeData(wb, "variables", data_table, headerStyle = header_style)
  
  openxlsx::addWorksheet(wb, "description")
  header_style <- openxlsx::createStyle(textDecoration = "Bold")
  openxlsx::writeData(wb, "description", second_page, headerStyle = header_style)
  
  openxlsx::saveWorkbook(wb, fname)
  
}
```

## Second page definitions

```{r, warning=T, echo=eval_debug, eval=T}
second_page_projects <- data.frame(variable=c("project_id",
                                               "project_name",
                                               "description",
                                               "extended_metadata",
                                               "people",
                                               "responsible",
                                               "comment"),
                                    description=c("Project identifier.",
                                                  "Lay name of the project.",
                                                  "Short description of the project.",
                                                  "Content of the more infornationin the sampling_comment column of mfd_db.",
                                                  "Research patner(s).",
                                                  "Person responsible for the project.",
                                                  "Comment to the project"))

second_page_db <- data.frame(
  variable = c(
    "fieldsample_barcode",
    "project_id",
    "sampling_method",
    "sampling_date",
    "latitude",
    "longitude",
    "habitat_typenumber",
    "sitename",
    "mfd_sampletype",
    "mfd_areatype",
    "mfd_hab1",
    "mfd_hab2",
    "mfd_hab3",
    "coords_reliable",
    "cell.10km_representative",
    "cell.10km",
    "cell.1km",
    "BioProject",
    "BioSample",
    "Metagenome",
    "Metagenome_assembly",
    "EUK_operon",
    "BAC_operon",
    "UMI_16SrRNA",
    "sampling_comment",
    "extraction_method",
    "extraction_id1",
    "extraction_id2",
    "extractionplate_id1",
    "extractionplate_id2",
    "extraction_row1",
    "extraction_row2",
    "extraction_col1",
    "extraction_col2",
    "extraction_conc1",
    "extraction_conc2",
    "library_method",
    "library_id1",
    "library_id2",
    "libraryplate_id1",
    "libraryplate_id2",
    "library_row1",
    "library_row2",
    "library_col1",
    "library_col2",
    "library_conc1",
    "library_conc2",
    "sequencing_method",
    "sequencing_id1",
    "sequencing_id2",
    "internal_name",
    "before_total_reads",
    "after_total_reads",
    "passed_filter_reads",
    "corrected_reads",
    "low_quality_reads",
    "too_many_N_reads",
    "too_short_reads",
    "too_long_reads",
    "before_total_bases",
    "before_q20_bases",
    "before_q30_bases",
    "after_total_bases",
    "after_q20_bases",
    "after_q30_bases",
    "corrected_bases",
    "before_read1_mean_length",
    "before_read2_mean_length",
    "after_read1_mean_length",
    "after_read2_mean_length",
    "before_q20_rate",
    "before_q30_rate",
    "after_q20_rate",
    "after_q30_rate",
    "duplication_rate",
    "before_gc_content",
    "after_gc_content",
    "peak_length"),
  description = c(
    "MFD sample identifier.",
    "Project identifier.",
    "Sampling method.",
    "Sampling Date.",
    "Latitude.",
    "Longitude.",
    "Four digit code associated to the samples' habitats. It encodes mfd_hab1, mfd_hab2 and mfd_hab3 for any given combination of mfd_sampletype and mfd_areatype.",
    "Lay name of the sampling site.",
    "Sample type (level 1 of the MFD ontology.)",
    "Area type (level 2 of the MFD ontology); it has to be used in combination with mfd_sampletype.",
    "Descriptor 1 of the habitat (level 3 of the MFD ontology); it has to be used in combination with mfd_sampletype and mfd_areatype",
    "Descriptor 2 of the habitat (level 4 of the MFD ontology); it has to be used in combination with mfd_sampletype, mfd_areatype and mfd_hab1.",
    "Descriptor 3 of the habitat (level 5 of the MFD ontology); it has to be used in combination with mfd_sampletype, mfd_areatype, mfd_hab1 and mfd_hab2.",
    "Note on the reliability od the coordinates: the possible values are Yes and No.",
    "Note on whether the sample was selected as a 10 km grid representative: the possible values are Yes and No.",
    "Cell code of the 10km reference grid of Denmark; used for subsampling if necessary.",
    "Cell code of the 1km reference grid of Denmark; used for subsampling if necessary.",
    "Accession identifier for the BioProject on NCBI.",
    "Accession identifier for the BioSample on NCBI.",
    "Accession identifier for the Metagenome on SRA. If the accession identifier is not reported, there are not data of this type for the sample.",
    "Accession identifier for the metagenome assembly on Zenodo https://zenodo.org/records/12605769.",
    "Accession identifier for the Eukaryotic Operon amplicons on SRA. If the accession identifier is not reported, there are not data of this type for the sample.",
    "Accession identifier for the Bacterial Operon amplicons on SRA. If the accession identifier is not reported, there are not data of this type for the sample.",
    "Accession identifier for the 16S rRNA UMI sequences on SRA. If the accession identifier is not reported, there are not data of this type for the sample.",
    "Comment on the sample; it might contain other unprocessed data.",
    "Extraction method.",
    "ExtractionID 1; Formatted as EXT-JOURNAL-Plateposition.",
    "ExtractionID 2; All samples on the project were only extracted once. If not NA this means that the extracted DNA was moved to this plate as part of the resequencing.",
    "Barcode of extraction plate 1; Formatted as EXTXXXXX.",
    "Barcode of extraction plate 2; Formatted as REPREPX, to indicate that they are not new extractions.",
    "Sample row position in extraction plate 1.",
    "Sample row position in extraction plate 2.",
    "Sample column position in extraction plate 1.",
    "Sample column position in extraction plate 2.",
    "Concentration of extracted DNA in ng/µL in extraction plate 1.",
    "Concentration of extracted DNA in ng/µL in extraction plate 2.",
    "Metagenomic library method.",
    "LibraryID 1; Formatted as LIB-JOURNAL-Plateposition.",
    "LibraryID 2; Formatted as LIB-JOURNAL-Plateposition.",
    "Barcode of library plate 1; Formatted as LIBXXXXX.",
    "Barcode of library plate 2; Formatted as REPREPX, to indicate that they are not new extractions.",
    "Sample row position in library plate 1.",
    "Sample row position in library plate 2.",
    "Sample column position in library plate 1.",
    "Sample column position in library plate 2.",
    "Concentration of final metagenomic libraries in ng/µL in library plate 1.",
    "Concentration of final metagenomic libraries in ng/µL in library plate 2.",
    "Sequencing method.",
    "SequencingID 1; Formatted as LIB-JOURNAL-Plateposition-Lane.",
    "SequencingID 2; Formatted as LIB-JOURNAL-Plateposition-Lane.",
    "Name used internally on the AAU HPC cluster.",
    "Total number of reads (R1 + R2) before quality trim and filtering.",
    "Total number of reads (R1 + R2) after quality trim and filtering.",
    "Number of reads passing all filters.",
    "Number of reads corrected by overlap analysis.",
    "Number of reads filtered due to poor quality (mean quality <= Q30).",
    "Number of reads filtered due to too many ambigious bases.",
    "Number of too short reads (length <= 100 bp).",
    "Number of too long reads.",
    "Total number of bases (R1 + R2) before quality trim and filtering.",
    "Q>20 bases before quality trim and filtering.",
    "Q>30 bases before quality trim and filtering.",
    "Total number of bases (R1 + R2) after quality trim and filtering.",
    "Q>20 bases after quality trim and filtering.",
    "Q>30 bases after quality trim and filtering.",
    "Number of bases corrected by overlap analysis.",
    "Average number of bp of R1 before quality trim and filtering.",
    "Average number of bp of R2 before quality trim and filtering.",
    "Average number of bp of R1 after quality trim and filtering.",
    "Average number of bp of R2 after quality trim and filtering.",
    "Rate of Q>20 bases before quality trim and filtering.",
    "Rate of Q>30 bases before quality trim and filtering.",
    "Rate of Q>20 bases after quality trim and filtering.",
    "Rate of Q>30 bases after quality trim and filtering.",
    "Rate of duplication of the reads (reads are deduplicated).",
    "Average GC content before quality trim and filtering.",
    "Average GC content after quality trim and filtering.",
    "Estimated peak insert size."))
```

### Write projects
```{r, warning=T, echo=eval_debug, eval=T}
print_meta(data_table = mfd_projects,
           fname = paste0(reformat.metadata.path, "/mfd_projects_test.xlsx"),
           second_page = second_page_projects)
```

### Write mfd db
```{r, warning=T, echo=eval_debug, eval=T}
print_meta(mfd_db,
           fname = paste0(reformat.metadata.path, "/mfd_db_test.xlsx"),
           second_page = second_page_db)
```

## Write releases

### Write projects map
```{r, warning=T, echo=eval_debug, eval=eval_release}
print_meta(data_table = mfd_projects,
           fname = paste0(releases.path, "/", Sys.Date(), "_mfd_projects.xlsx"),
           second_page = second_page_projects)

if(file.exists(paste0(releases.path, "/latest_mfd_projects.xlsx"))){
  file.remove(paste0(releases.path, "/latest_mfd_projects.xlsx"))
}
print_meta(data_table = mfd_projects,
           fname = paste0(releases.path, "/latest_mfd_projects.xlsx"),
           second_page = second_page_projects)
```

### Write mfd db
```{r, warning=T, echo=eval_debug, eval=eval_release}
print_meta(data_table = mfd_db,
           fname = paste0(releases.path, "/", Sys.Date(), "_mfd_db.xlsx"),
           second_page = second_page_db)

if(file.exists(paste0(releases.path, "/latest_mfd_db.xlsx"))){
  file.remove(paste0(releases.path, "/latest_mfd_db.xlsx"))
}
print_meta(data_table = mfd_db,
           fname = paste0(releases.path, "/latest_mfd_db.xlsx"),
           second_page = second_page_db)
```